Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-12 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

Recall that given a set of intervals\nb$\mathscr{I}$, we want to
know whether there is an QIVPM mapping to $\mathscr{I}$. If there
is a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we want
to verify whether $\bar{\mu}$ has a non-empty core. Usually, the
easiest way to prove the existence is to construct an example. As
in example~\ref{ex:three-dimensional-5-value}, constructing a QIVPM
directly is long and tedious. In contrast, a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$
can be easily constructed by the Born rule. Therefore, it would be
desirable if we can construct a QIVPM\nb$\bar{\mu}$ from $\mu$,
and expect $\mu$ is in the core of $\bar{\mu}$.

@@

Although a QIVPM can be constructed by an additive pair easily, a
convex pair may not give a convex QIVPM with non-trivial finite number
of intervals. Notice a Wright-convex function is midpoint-convex or
Jensen-convex, i.e., 
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
\end{equation}
and a midpoint-convex function is continuous on an open interval if
we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
Therefore, for any convex QIVPM constructed by a convex pair\nb$\left(\mathscr{I},\iota\right)$,
$\mathscr{I}$ must either be $\left\{ \necess,\imposs,\unknown\right\} $
or contain infinitely many intervals.

>>>>

Recall that given a set of intervals\nb$\mathscr{I}$, we want to
know whether there is an QIVPM mapping to $\mathscr{I}$. If there
is a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we want
to further verify whether $\bar{\mu}$ has a non-empty core. Usually,
the easiest way to prove the existence is to construct an example.
As in example~\ref{ex:three-dimensional-5-value}, constructing a
QIVPM directly is long and tedious. In contrast, a quantum probability
measure\nb$\mu:\events\rightarrow\left[0,1\right]$ can be easily
constructed by the Born rule. Therefore, it would be desirable if
we can construct a QIVPM\nb$\bar{\mu}$ from $\mu$, and expect $\mu$
is in the core of $\bar{\mu}$.

@@

Although a QIVPM can be constructed by an additive pair easily, a
convex pair may not give a convex QIVPM with non-trivial finite number
of intervals. Notice a Wright-convex function is midpoint-convex or
Jensen-convex, i.e., 
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
\end{equation}
and a midpoint-convex function is continuous on an open interval if
we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
Therefore, for any convex pair\nb$\left(\mathscr{I},\iota\right)$,
$\mathscr{I}$ must either be $\left\{ \necess,\imposs,\unknown\right\} $
or contain infinitely many intervals.

Although a pair\nb$\left(\mathscr{I},\iota\right)$ is not convex,
it can still induce a convex QIVPM. In particular, every QIVPM on
a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
The next natural question is whether a non-convex pair always induces
some non-convex QIVPM, and the answer is ``yes'' by the following
lemma.

\begin{lemma}Given an additive but non-convex pair\nb$\left(\mathscr{I},\iota\right)$,
there is a non-convex quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$.\end{lemma}

\begin{proof}Since $\left(\mathscr{I},\iota\right)$ is additive
but non-convex, there are three numbers\nb$x_{0}$, $x_{1}$, and
$x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
Consider a 4-dimensional Hilbert space and a density matrix
\begin{equation}
\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\textrm{ .}
\end{equation}
Let $P_{0}=\proj{0}+\proj{2}$, $P_{1}=\proj{1}+\proj{2}$, and $\bar{\mu}(P)=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(P)\right)$.
Then,
\begin{equation}\eqalign{ 
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)
=\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0}+\proj{1}+\proj{2})\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{2})\right)\\ 
= & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)
\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\\ 
= & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{0}+\proj{2})\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}(\proj{1}+\proj{2})\right)
=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ .} 
}\end{equation}
\end{proof}
